Probabilistic Programming around Gaussian Processes

### 2019-10-24 abstract/paper.tex
better language

In this work, we advocate a third approach, which combines
advantages of the other two above. We present an architecture of
a Gaussian process library that provides an efficient
implementation of Gaussian process-related computations shared
by all algorithms, but lets program, virtually without
restrictions, both Gaussian process kernels and probabilistic
models of uncertainty, and combine Gaussian processes and
probabilistic models for inference using algorithms supported by
the framework. Our implementation of probabilistic
programming-enabled Gaussian processes, GoGP
(\url{http://bitbucket.org/dtolpin/gogp}), is written in Go
and makes extensive use of modelling and inference capabilities
provided by Infergo~\cite{T19}, a Go library for differentiable
probabilistic programming. In what follows we first outline GoGP
design  and then illustrate the use of GoGP on a number of case
studies inspired by applications.

>>>>

In this work, we advocate a third approach, which combines
advantages of the other two above. We present an architecture of
a Gaussian process library that provides an efficient
implementation of Gaussian process-related computations shared
by all algorithms, but lets program, virtually without
restrictions, both Gaussian process kernels and probabilistic
models of uncertainty, and combine Gaussian processes and
probabilistic models for inference by means of inference
algorithms supported by the framework. Our implementation of
probabilistic programming-enabled Gaussian processes, GoGP
(\url{http://bitbucket.org/dtolpin/gogp}), is written in Go and
makes extensive use of modelling and inference capabilities
provided by Infergo~\cite{T19}, a Go library for differentiable
probabilistic programming. In what follows we first outline GoGP
design  and then illustrate the use of GoGP on a number of case
studies inspired by applications.
